Timely Object Detection

### 2012-03-05 writeups/eccv12/eccv12.tex
almost there

\mainmatter
\def\ECCV12SubNumber{***}  % Insert your submission number here

@@

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Cras imperdiet, orci sagittis consequat vehicula, metus tellus pulvinar metus, eget cursus tortor quam sit amet ligula. Donec vel leo ac sem blandit vulputate. Etiam pellentesque, quam non condimentum posuere, dolor augue mollis velit, posuere auctor lectus neque in nulla. Aenean in risus sit amet nisl lacinia eleifend et non velit. Aliquam mi magna, faucibus sed venenatis vitae, commodo ac nisi. Pellentesque tristique dictum mauris, et sollicitudin eros sollicitudin id. Cras elit mi, luctus quis vestibulum in, sagittis vel elit. Sed ligula dolor, ultrices eget gravida sit amet, dictum vel nisl.
\end{abstract}

>>>>

\mainmatter
\def\ECCV12SubNumber{1617}  % Insert your submission number here

@@

\begin{abstract}
In a large, multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

### 2012-03-05 writeups/eccv12/technical.tex
almost there

The final evaluation of a policy consists of the area under the performance vs. time curve.
Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.
Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

\subsubsection{Reward: decrease in mean entropy}
We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$.
As with the above policy, the decrease in entropy is considered with regard to the time of the action.

@@

\todo{Describe the greedy thing and the generalized policy iteration that we do.}

>>>>

The final evaluation of a policy consists of the area under the performance vs. time curve.
Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.

Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

\todo{explain the behavior}

\subsubsection{Reward: decrease in mean entropy}
We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$: $\frac{1}{K}\sum_{k=1}^K H(C_k)$, where $H(C_k) = - \sum_{c_k \in {0,1}} P(c_k) \log P(c_k)$.
We follow the same setup as above, but strive to maximize the area \emph{above} the curve of mean entropy vs. time.

@@

The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be $[P(C_k), \, H(C_k), \, 1]$.

Our procedure for learning the weights is standard generalized policy iteration \cite{Sutton1998}.
We first initialize the weights $\theta$ to the heuristic value function of simply picking the maximum $P(C_k)$: $\theta_i = [1, \,0, \,0]$.

With this policy, we gather $N$ recognition episodes.
We formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$ that were seen in the gathered episodes, and a vector $y$ consisting of the individual rewards.
We then solve the system $\Phi \theta = y$.

\todo{more}
